Astr 513: Homework 2

### 2016-03-10 HW2/HW2.tex
Added part c graphs, finished tex file, final pdf

\section{Part C}
\label{sec:partC}

@@

We can marginalize over any two parameters to acquire the third.
See \autoref{sec:partE} for figures showing these distributions 
with no priors.

\section{Part E}
We can also introduce logarithmic priors
\begin{equation*}
  \label{eq:log_prior}
  P_{pr}(X) \propto x^{-1}
\end{equation*}
on any of our parameters. The effect is to shift (sometimes slightly)
the distributions down slightly. In the following three figures
we plot the marginalized probability for each parameter with and 
without a logarithmic prior. These probabilities were generated
by performing a numerical integral over each of the marginalized
parameters.

@@

\newpage

\section*{References}

>>>>

\section{Part C}
\label{sec:partC}
The analytic approach to this problem involves a Jacobian transformation from $(R,h,g)$ to $(u_x,u_y,g)$. To do so, we invert 
\[ h=\frac{u_y^2}{2g} \ \ \textrm{and} 
\ \ R=\frac{2u_xu_y}{g} \] to give 
\[ u_x= \sqrt{2gh} \ \ \textrm{and} 
\ \ u_y=\sqrt{\frac{g}{8h}} .\]
Of course, $g=g$. The probability distribution is 
\begin{equation}
  P(R,h,g)dRdhdg=P(u_x,u_y,g)du_xdu_ydg.
\end{equation}
It can be written in terms of three Gaussian functions 
\begin{equation}
  P(R,h,g)=G(R,R_0,\sigma_R)G(h,h_0,\sigma_h)G(g,g_0,\sigma_g).
\end{equation}
The Jacobian transformation of the probability distribution is 
\begin{equation}
  P(u_x,u_y,g) = G(R,R_0,\sigma_R)G(h,h_0,\sigma_h)G(g,g_0,\sigma_g) J\bigg(\frac{R,h,g}{u_x,u_y,g}\bigg)
\end{equation}
where $J$ is the Jacobian. In this transformation from 3 variables to 3 inferences, 
\begin{equation}J=
\begin{vmatrix}
  \frac{\partial R}{\partial u_x} & \frac{\partial R}{\partial u_y} & \frac{\partial R}{\partial g}\\
  \frac{\partial h}{\partial u_x} & \frac{\partial h}{\partial u_y} & \frac{\partial h}{\partial g}\\
  \frac{\partial g}{\partial u_x} & \frac{\partial g}{\partial u_y} & \frac{\partial g}{\partial g}\\
\end{vmatrix}= \frac{2u_y^2}{g^2}. 
\end{equation}
With the Jacobian, 
\begin{eqnarray}\nonumber
P(u_x,u_y,g)&=& \frac{u_y^2}{\sqrt{2}\pi^{3/2} \sigma_R \sigma_h \sigma_g g^2}\textnormal{exp}\bigg[{\frac {-(\frac{2u_yu_x}{g}-R_0)^2}{2 {\sigma_R} ^2}}\bigg]\\
&& \textnormal{exp}\bigg[{\frac {-(\frac{u_y^2}{2g}-h_0)^2}{2 {\sigma_h} ^2}}\bigg]\textnormal{exp}\bigg[{\frac {-(g-g_0)^2}{2 {\sigma_g} ^2}}\bigg].
\end{eqnarray}
In order to obtain the probability distribution of $u_y$, we need to marginalize Equation 9 over $u_x$ and $g$. Thus, 
\begin{eqnarray}\nonumber
P(u_y)&=& \frac{u_y^2}{\sqrt{2}\pi^{3/2} \sigma_R \sigma_h \sigma_g}\textnormal{exp}\bigg[{\frac {-(\frac{u_y^2}{2g}-h_0)^2}{2 {\sigma_h} ^2}}\bigg]\\
&&\int_{-\infty}^{\infty}\int_{-\infty}^{\infty}\textnormal{exp}\bigg[{\frac {-(\frac{2u_yu_x}{g}-R_0)^2}{2 {\sigma_R} ^2}}\bigg]\textnormal{exp}\bigg[{\frac {-(g-g_0)^2}{2 {\sigma_g} ^2}}\bigg]\frac{1}{g^2}du_xdg. 
\end{eqnarray}
In order to obtain the probability distribution of $u_x$, we need to marginalize Equation 9 over $u_y$ and $g$. Thus, 
\begin{eqnarray}\nonumber
P(u_x)&=& \frac{1}{\sqrt{2}\pi^{3/2}\sigma_R \sigma_h \sigma_g} \int_{-\infty}^{\infty}\int_{-\infty}^{\infty} \textnormal{exp}\bigg[{\frac {-(\frac{u_y^2}{2g}-h_0)^2}{2 {\sigma_h} ^2}}\bigg]\\
&& \textnormal{exp}\bigg[{\frac {-(\frac{2u_yu_x}{g}-R_0)^2}{2 {\sigma_R} ^2}}\bigg]\ \textnormal{exp}\bigg[{\frac {-(g-g_0)^2}{2 {\sigma_g} ^2}}\bigg]\frac{u_y^2}{g^2}du_ydg. 
\end{eqnarray}
As seen in \autoref{fig:ux_analytic} and \autoref{fig:uy_analytic}, the shapes of the analytic probability distributions match the shapes of the probability distributions from Monte Carlo simulations.

\begin{figure}[ht]
  \centering
  \includegraphics[keepaspectratio]{ux_analytic.pdf}
  \caption{The analytic, marginalized probability of $u_x$. The marginalization
    over the other two parameters was done numerically.}
  \label{fig:ux_analytic}
\end{figure}

\begin{figure}[ht]
  \centering
  \includegraphics[keepaspectratio]{uy_analytic.pdf}
  \caption{The analytic, marginalized probability of $u_y$. The marginalization
    over the other two parameters was done numerically.}
  \label{fig:uy_analytic}
\end{figure}

@@

We can marginalize over any two parameters to acquire the third.
See \autoref{fig:ux_bayesian}\autoref{fig:uy_bayesian} for figures showing these distributions 
with no priors.

\section{Part E}
\label{sec:partE}
We can also introduce logarithmic priors
\begin{equation*}
  \label{eq:log_prior}
  P_{pr}(X) \propto x^{-1}
\end{equation*}
on any of our parameters. The effect is to shift (sometimes slightly)
the distributions down slightly. In the following three figures
we plot the marginalized probability for each parameter with and 
without a logarithmic prior. These probabilities were generated
by performing a numerical integral over each of the marginalized
parameters.

@@
